An early warning system for monitoring stress in the financial system

### 2016-10-09 srisk9 copy.tex
Lots and lots of changes
Latest

\documentclass[12pt]{article}
\usepackage{amsmath}
\usepackage{graphicx,psfrag,epsf,comment}
\usepackage{enumerate}
\usepackage{natbib}
\usepackage{url} % not crucial - just used below for the URL 
\bibliographystyle{chicago}
\usepackage{threeparttable}

%\pdfminorversion=4
% NOTE: To produce blinded version, replace "0" with "1" below.
\newcommand{\blind}{0}

% DON'T change margins - should be 1 inch all around.
\addtolength{\oddsidemargin}{-.5in}%
\addtolength{\evensidemargin}{-.5in}%
\addtolength{\textwidth}{1in}%
\addtolength{\textheight}{1.3in}%
\addtolength{\topmargin}{-.8in}%

\newcommand{\logit}{\mathrm{logit}}
\newcommand{\I}{\mathrm{I}}
\newcommand{\E}{\mathrm{E}}
\newcommand{\p}{\mathrm{P}}
\newcommand{\e}{\mathrm{e}}
\renewcommand{\o}{\omega}
\newcommand{\vecm}{\mathrm{vec}}
\newcommand{\kp}{\otimes}
\newcommand{\diag}{\mathrm{diag}}
\newcommand{\cov}{\mathrm{cov}}
\newcommand{\eps}{\epsilon}
\newcommand{\ep}{\varepsilon}
\newcommand{\obdots}{\ddots}    % change this later
\newcommand{\Ex}{{\cal E}}
\newcommand{\Ax}{{\mathrm{A}}}
\newcommand{\Exd}{\Ex_d}
\newcommand{\Es}{\widetilde\E}
\newcommand{\rat}{{\frac{c_{ij}}{c_{i,j-1}}}}
\newcommand{\rmu}{m}
\newcommand{\rsig}{  r}
\newcommand{\fd}{\mu}
\newcommand{\tr}{\mathrm{tr}}
\newcommand{\cor}{\mathrm{cor}}
\newcommand{\bx}[1]{\ensuremath{\overline{#1}|}}
\newcommand{\an}[1]{\ensuremath{a_{\bx{#1}}}}

@@

%\bibliographystyle{natbib}

\def\spacingset#1{\renewcommand{\baselinestretch}%
{#1}\small\normalsize} \spacingset{1}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\if0\blind
{
  \title{\bf Monitoring  risk in the financial system using time series methods}
  \author{Piet de Jong\thanks{
    The authors gratefully acknowledge CIFR, the Centre of International Financial Regulation for financial support and other assistance.}\hspace{.2cm}\\
    Department of Applied Finance and Actuarial Studies, Macquarie University\\
    and \\
    Geoffrey Loudon\\
    Department of Applied Finance and Actuarial Studies, Macquarie University\\
    and\\
    Weihao Choo\\
    Department of Applied Finance and Actuarial Studies, Macquarie University}
  \maketitle
} \fi

\if1\blind
{
  \bigskip
  \bigskip
  \bigskip
  \begin{center}
    {\LARGE\bf Measuring baseline and systemic risk using financial time series}
\end{center}
  \medskip
} \fi

\bigskip
\begin{abstract}
SRISK methodology recently proposed in the literature is refined and extended.  The refinement is to define  systemic risk using a formalised stress testing framework including a stress function.  Baseline risk and the stress risk  are in terms of the  ordinary and stressed expectation.  Stressed expectation is expectation computed  under a hypothetical  stress, modelled with the stress function and scenarios.  Systemic stress is defined in terms of a stress function and systemic scenarios impacting on a number of firms or financial entities.  Stress functions are chosen by the practitioner and typically exaggerate undesirable extreme outcomes.    Properties and characterisations of stress and stress related quantities are displayed and explored.     Application is made to the study of the stability of Australian banks using daily time series data.
\end{abstract}

\noindent%
{\it Keywords:}  Capital shortfall, baseline risk, stress testing,  stressed expectation, stress diversification.
\vfill

\newpage
\spacingset{1.45} % DON'T change the spacing!

\section{Introduction}\label{intro}
Monitoring stresses and systemic risk in the financial system is a key function of macro--prudential regulation. Central banks and other financial regulatory bodies such as the US Financial Stability Oversight Council, the European Systemic Risk Board and the Australian Prudential Regulation Authority (APRA) are concerned with developing and applying early warning quantitative  measures  to warn of potential episodes of heightened systemic risk. Systemic risk has many dimensions. For example, in their influential review paper, \cite{Bisias2012} present a taxonomy of six categories of systemic risk comprising 31 quantitative risk measures. While attempts to gain consensus on a theoretical definition have proved elusive, several empirical measures of systemic risk have been developed and applied with  success.  An important example is the SRISK measure due to \cite{brownlees2015} -- an index that measures the expected capital shortfall of a financial institution conditional on a large and lengthy decline in equity markets. \cite{brownlees2015} show that their SRISK based measures are able to identify systemically important financial firms and are informative about the impact of financial crises on future macro-economic conditions.

This paper refines and extends the SRISK model of \cite{brownlees2015} in  key ways. First, their SRISK measure is refined  as a put on the expected shortfall.   Second, the ordinary expectation of is defined as the baseline risk (\br) associated with the put.   Using a stress function  the so--called stressed expectation is used to characterise the expectation given a stress.   Stressed expectation can be similar to the \cite{brownlees2015} conditional expectation given  a severe market downturn.  However our generalised methodology  permits a far more flexible definition of stress and a wider class of ``stressors" including stress defined in terms of  a number of extreme outcomes.  The difference between the stressed and ordinary expectation is defined as the risk associated with the stress, called \pr\ where PSI refers the function modelling the stress.

@@

\cite{brownlees2015} define stress by conditioning on an absolute cutoff of arbitrary size and length. Our development suggests  it is also helpful to specify conditional behaviour in percentile terms relative to current market conditions. This yields a sharper focus on the incremental impact of further stress and permits a more incisive view of the  implications from SRISK numbers. These extensions provide additional insights into the sources and economic nature of for example systemic risk. The measures provide potentially new and improved ways of anticipating episodes of heightened systemic risk. Their practical use can be expected to help regulators monitor risk including systemic risk and contagion in timely fashion,   facilitating remedial action where necessary.

@@

To demonstrate the nature and usefulness of our measures, we use publicly available daily financial data for the eight Australian banks detailed in \tref{eightbanks} spanning the period from  3 April 2000 through to 1 December 2014.  The data is described in detail in \aref{data}.  Prices, adjusted for dividends are plotted in \fref{prices}.  Prices are combined with number of shares to derive total equity. Total debt for each firm is also collected from annual accounting reports.

Remaining sections are structured as follows. Section \ref{litrev} briefly discusses related literature. Section \ref{capshort} and \ref{futshort} define current and future  capital shortfall similarly as \cite{brownlees2015} under a simple Basel II regulatory framework. The definition of systemic risk used by \cite{brownlees2015} is discussed in \sref{srisk}, and is refined and extended in \sref{improve}. Applications to Australian bank data are discussed in \sref{simulate} and \sref{simulate1}. Section \ref{aggregate}  discusses the aggregation of  stresses across firms with and without allowance for merging or diversification. Section \ref{monitoring} displays stress calculations as they would proceed in real time.   Section \ref{riskmethod} offers an alternative modelling approach, based on assets.  Section \ref{conclude} concludes.

@@

\begin{figure}[htbp]
\label{prices}
\begin{center}
\includegraphics[width=16cm]{figures/prices.pdf}
\caption{Daily stock  prices of four major (left panel) and four minor (right panel) Australian banks 2000--2014.  Price series normalised to start at 1.}
\end{center}
\end{figure}

@@

\cite{brownlees2015} further develop the empirical methodology to construct SRISK measures. SRISK depends on the firm's size, leverage and its LRMES. The LRMES is obtained by assuming a dynamic process for the joint distribution of firm and market returns. \cite{brownlees2015} use  the standard GARCH-DCC model of \cite{engle2002dynamic} with threshold ARCH volatilities on the basis that this represents a good trade-off between model complexity and prediction accuracy. The LRMES is computed as the Monte Carlo average of simulated multi-period returns,  conditional on the return being worse than the cut-off level chosen to identify a financial crisis. Using a sample of large US financial firms,  \cite{brownlees2015} show the practical usefulness of their measure in three ways: (i) SRISK rankings identify systemically risky US banks during the GFC; (ii) pre-crisis SRISK helps predict capital injections by the Fed Reserve; (iii) aggregate SRISK provides early warning of declines in industrial production and higher unemployment.

\cite{Engle2015} extend the model in \cite{brownlees2015} to incorporate global, country and industry effects. This extended model makes  use of \cite{Engle2014dcb}'s dynamic conditional beta model. Their empirical methods are able to provide information about the relative systemic importance of industry type and country identity. For instance, they find  that systemic risk in Europe during the GFC was predominantly due to banks while France and the UK recorded the largest country-level SRISK numbers.

\cite{adrian2011covar} propose an alternative measure of systemic risk that emphasises the co-dependence of financial firms and the importance of risk spillovers within the financial sector. They introduce CoVaR$_i$ which computes the Value-at-Risk (VaR) of the entire financial system, conditional on institution $i$ being in distress. Distress is defined as the state where the institution is exactly at its VaR level. \cite{Girardi2013} improve CoVaR by conditioning on the institution being at most at its VaR. This generalisation is useful as it takes into account the severity of tail losses and facilitates back-testing of CoVaR.

@@

Empirical estimates of SRISK  requires a model for the joint distribution of returns of individual firms and the market. Many of these papers use \cite{engle2002dynamic}'s GARCH-DCC model aiming to capture the time-varying dynamics of the return (co)variances in a feasible manner. While we also use this model in our empirical analysis, we emphasize that our approach can utilise any appropriate model for simulating the joint distribution of firm and market returns going forward.

\section{Capital shortfall and leverage}\label{capshort}

@@

The definition of capital shortfall in \eref{shortfall} is restrictive if not simplistic.   It is used here to conform to the previous literature and provide an easily accessible  platform to the key results of this paper,  without becoming entangled in precise and perhaps more realistic definitions of shortfall.   Indeed \sref{riskmethod} deals with a more realistic and intricate definition.

@@

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=16cm]{figures/bloglev.pdf}
\caption{Adjusted log--leverages for four major (left panel) and four minor (right panel) Australian banks from the beginning of 2003 through to end of 2014.  All banks contravene the threshold (corresponding to the zero horizontal) around the start of 2009.}\label{Bloglev}
\end{center}
\end{figure}

\section{Future capital shortfall}\label{futshort}

@@

The actual capital shortfall is $S^+$, the positive part of $S$:
\be{bs}
S^+ = kd (1-\e^{r-\ell})^+\ .
\ee
Thus $S^+$ is $kd$ times a put on the return $\e^{r-\ell}$ with strike 1.  There is a future shortfall if $r<\ell$.  Default put options similar to \eref{bs} have been discussed in the insurance literature as critical to an evaluation of a firm:  see for
example \citet{merton1977analytic}, \citet{doherty1986price}, \citet{cummins1988risk}, \citet{myers2001capital} and \citet{sherris2006solvency}.

To illustrate the setup, \fref{simulation}   displays two snapshot outputs from projections generated as described  in \aref{garchdcc}:  6000  simulated one month ahead projected returns for  CBA and the wider market, on  two dates: the first trading day in January 2009 and the first trading day in December 2014.  The CBA returns are used to calculate the future shortfall per units $kd$ as in \eref{fshortfall}.  Both panels use the same horizontal and vertical scales.   Thus based on the available data at those two points in  time, policy makers and regulators faced entirely different projections based on the same time series model.   The scatter of dots are the forward simulations.  Note there is no hindsight bias as the model at each time point is based on the available data to that point in time.     In the left panel $S>0$ for most scenarios.    In the right panel $S<0$ for any conceivable market scenario.

 The black dots in each panel indicate the actual outcome after one month.    In the left panel the outcome is a decline in both  the market and CBA stock price.    In the right panel there is slight decline in the stock price, and a more substantial market downturn.    Thus at the beginning of January  2009 CBA was projected to be far from compliance in a month while in December 2014 the one month projection is of complete compliance.

 The two panels  display very different volatility and slopes. In January 2009 both CBA and market return distributions are highly volatile and correlated. The correlation remains strong in December 2014 but with less return volatility. These snapshots are used to compute baseline and systemic stresses shown in subsequent sections.

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=16cm]{figures/figCBA.pdf}
\caption{Forecast bivariate distribution of future shortfall $S$ per unit $kd$  for CBA (vertical axis) and market rate of return (horizontal axis) at start of January 2009 (left panel)  and December 2014 (right panel). Note scales in both panels are the same, the relatively large volatility in the left panel, and the left skew in the  marginal distributions.  Black dots indicate actual  outcome at the end of the month.}\label{simulation}
\end{center}
\end{figure}

\section{Systemic risk SRISK}\label{srisk}

 \cite{brownlees2015} defines  systemic risk for a group of firms  at a particular point of time as
\be{esrisk}
\sr\equiv \sum_i \left\{\Es(S_i)\right\}^+ \ ,
\ee
where $S_i$ refers to the future shortfall in firm $i$.   Further  $\Es$ denotes expectation given a major general market downturn. Hence the expected capital shortfall (allowing surplus offset) is computed from \eref{fshortfall} assuming a market downturn and added across all firms. Firms with an expected capital surplus under stress are ignored.

The systemic risk of firm $i$ at a particular point of time is defined by \cite{brownlees2015} as the proportionate contribution \eref{esrisk}:
\be{sriskperc}
\sr_i\equiv\frac{\{\widetilde\E(S_i)\}^+}{\sr}\ .
 \ee
Large $\mathrm{SRISK}_{i}$ indicates firm $i$ is systemically important: it holds a high proportion of the total debt, and it is likely to heavily breach the Basel capital requirement compared to remaining other firms.  Expression \eref{sriskperc} depends on $k$ through each of the adjusted log--leverages $\ell_i$.   Given a general market downturn, the values $\{\Es(S_i)\}^+$  in \eref{sriskperc} are known:  there is no uncertainty except for possible  uncertainty in estimating the stressed conditional  expected value.

The above general setup  is subject to criticisms and improvements.  First, SRISK in \eref{sriskperc} can be modified to be based on $S_i^+$ the positive part of shortfall rather than the positive part of expected shortfall.   In many cases $\Es(S_i)=0$  and insensitive to actual shortfalls.   Second, the definition of $\Es$ is restrictive: a market downturn defined by a market downturn greater than 10\%.   Such a specific absolute downturn is unnecessarily arbitrary.  For example the downturn is more easily achieved  in a highly volatile environment and hence the stress response takes on different meanings depending on context.  Third as shown below the stressed expectation $\Es$ is composed of two parts, so--called baseline risk and change in expectation risk caused by the actual stress event.

\section{Improved systemic risk measurement}\label{improve}

This section describes a general framework for  systemic risk measurement.  The framework builds on and aims to improve on the techniques built into f \sr\ and $\sr_i$ in \eref{esrisk} and \eref{sriskperc}.   The framework assumes a response variable such as capital shortfall $S$ or $S^+$ for a firm or group of firm subjected to stress.  The  framework   puts ``stress testing" on a formal footing.

For notational convenience assume the response of interest is $S$ although this can be replaced with $S^+$ or some other function of $S$.  The framework is built up from the following parts:
\bi
\i  A stress function $\psi(\omega)\ge 0$ defined on scenarios $\omega$.       Scenarios $\omega$ can be discrete or continuous.   Further $\E(\psi)=1$ where expectation is across all scenarios.  Scenarios $\omega$ are systemic if they have potential impact on many firms.
\i  Baseline risk is defined as the ordinary expectation
$$
\br\equiv \E(S)\equiv\sum_\omega f(\omega) \E(S|\omega)\ ,
$$
where $f(\omega)$ denotes the ``real world" probabilities of different scenarios.    If the space of scenarios is continuous then $f(\omega)$ is a density and the  sum an integral.
\i Stressed expectation  is defined in terms of the stress function as
\be{formula}
\Es(S) \equiv \sum_\omega \psi(\omega) f(\omega)\E(S|\omega)=\E\{\psi\E(S|\psi)\}=\E(\psi S)=\E(S)+\cov(S,\psi)\ ,
\ee
where the last equality follows since $\E(\psi)=1$.  The import of $\psi(\omega)$ is to change the natural probabilities $f(\omega)$ to ``stressed" probabilities $\tilde f(\omega)\equiv \psi(\omega)f(\omega)$.   Note $\sum_\omega \tilde f(\omega)=\E(\psi)=1$. 
 \i $\psi$--risk is defined as the difference between baseline risk and stressed risk
 $$
 \pr \equiv \Es(S)-\E(S) = \cov(S,\psi)\cq \Es(S)=\br+\pr\ .
 $$
\ei

 A simple example is where $\psi(\omega)=0$ except for a single  scenario $\omega$ where it is equal to $1/f(\omega)$.   In this case all probability is transferred to the single scenario $\omega$ and $\Es(S)=\E(S|\omega)$.  The conditional expectation is often computed with a spreadsheet.

A richer example is where $\omega$ is the percentile of a variable such as the overall market return, measured relative to the currently applicable market return distribution.   Then $f(\omega)$ is the uniform density on the unit interval.   If 
$$
\psi(\omega)=n\{1-(1-\omega)^{n-1}\}\ ,
$$
then $\psi$ is the density of the worst percentile outcome in $n$ independent trials.   This stress function implies \pr\  corresponds to the increase in risk when the general market has its worst outcome in $n$ independent trials.  This stress function  is used to study stress in Australian banks in \sref{simulate1}.  If $n=1$ then $\psi(\omega)=1$, there is no stress, and $\Es(S)=\E(S)$ and \pr=0.

Another example, close to that implemented in \cite{brownlees2015} is where $\omega$ is a percentile with $\psi(\omega)=1/c$ for $\omega<c$ and 0 otherwise.   In this case  $\Es(S)=\E(S|\psi<c)$ and \pr\  is the difference between the  conditional tail and ordinary expectation.
More general stressed expectations of the form of \eref{formula} are discussed in \cite{furman2008weighted1} and \cite{choo2010determining}.

Both \br\ and \pr\ are linear and aggregate over firms.  For example
$$
\pr\left(\sum_iS_i\right) = \sum_i\pr\left(S_i\right)\ .
$$
Linearity is obvious for \br\ and for \pr\  follows from the linearity of covariance.

@@

\section{One month ahead forecast risk in individual banks}\label{simulate1}

>>>>

\documentclass[authoryear]{elsarticle}
\usepackage{amsmath}
\usepackage{graphicx,psfrag,epsf,comment}
\usepackage{enumerate}
\usepackage{url} % not crucial - just used below for the URL 
\bibliographystyle{chicago}
\usepackage{threeparttable}

\newcommand{\logit}{\mathrm{logit}}
\newcommand{\I}{\mathrm{I}}
\newcommand{\E}{\mathrm{E}}
\newcommand{\p}{\mathrm{P}}
\newcommand{\e}{\mathrm{e}}
\renewcommand{\o}{\omega}
\newcommand{\vecm}{\mathrm{vec}}
\newcommand{\kp}{\otimes}
\newcommand{\diag}{\mathrm{diag}}
\newcommand{\cov}{\mathrm{cov}}
\newcommand{\eps}{\epsilon}
\newcommand{\ep}{\varepsilon}
\newcommand{\obdots}{\ddots}    % change this later
\newcommand{\Ex}{{\cal E}}
\newcommand{\Ax}{{\mathrm{A}}}
\newcommand{\Exd}{\Ex_d}
\newcommand{\Es}{\Ex}
\newcommand{\rat}{{\frac{c_{ij}}{c_{i,j-1}}}}
\newcommand{\rmu}{m}
\newcommand{\rsig}{  r}
\newcommand{\fd}{\mu}
\newcommand{\tr}{\mathrm{tr}}
\newcommand{\cor}{\mathrm{cor}}
\newcommand{\bx}[1]{\ensuremath{\overline{#1}|}}
\newcommand{\an}[1]{\ensuremath{a_{\bx{#1}}}}

@@

\title{An early warning system for monitoring  stress in the financial system}
%\author[acst]{Piet de Jong\corref{cor1}\footnote{The authors gratefully acknowledge CIFR, the Centre of International Financial Regulation for financial support and other assistance}}
%\ead{piet.dejong@mq.edu.au}
%\author[acst]{Geoffrey Loudon}
%\author[acst]{Weihao Choo}
%\address[acst]{Department of Applied Finance and Actuarial Studies Macquarie University, NSW 2109, Australia.}
%\cortext[cor1]{Corresponding author}

\begin{abstract}
SRISK methodology recently proposed in the literature is refined and extended using a formalised stress testing framework and exploiting time series methods.  Baseline risk and the stress risk  are in terms of time series based ordinary and stressed expectation.  Stressed expectation is expectation computed  under a hypothetical  stress, modelled with a stress function and scenarios.  Systemic stress is defined in terms of stresses   impacting groups of firms or financial entities.  Stress functions are chosen by the practitioner and  exaggerate the probability undesirable  outcomes.    Properties and characterisations of stress and stress related quantities are displayed and explored.     Application is made to the study of the stability of Australian banks using daily time series data.
\end{abstract}

\date{}
\maketitle
\noindent
{\it Keywords:}  Capital shortfall, baseline risk, stress testing,  stressed expectation, stress diversification.

\newpage

\section{Introduction}\label{intro}
Monitoring stresses and systemic risk in the financial system is a key function of macro--prudential regulation. Central banks and other financial regulatory bodies such as the US Financial Stability Oversight Council, the European Systemic Risk Board and the Australian Prudential Regulation Authority (APRA) are concerned with developing and applying early warning quantitative  measures  to warn of potential episodes of heightened systemic risk.

Systemic risk has many dimensions. For example, in their influential review paper, \cite{Bisias2012} present a taxonomy of six categories of systemic risk comprising 31 quantitative risk measures. While attempts to gain consensus on a theoretical definition have proved elusive, several empirical measures of systemic risk have been developed and applied with  success.  An important example is the SRISK measure due to \cite{brownlees2015} -- an index that measures the expected capital shortfall of a financial institution conditional on a large and lengthy decline in equity markets. \cite{brownlees2015} show that their SRISK based measures are able to identify systemically important financial firms and are informative about the impact of financial crises on future macro-economic conditions.

This paper refines and extends the SRISK model of \cite{brownlees2015} in  key ways. First SRISK is formalised  as a put on the expected shortfall with the ordinary expectation defined as the baseline risk (\br) associated with the put.   Using a stress function  the so--called stressed expectation is used to measure the impact of stress.   Stressed expectation can be similar to the \cite{brownlees2015} conditional expectation given  a severe market downturn.  However our generalised methodology  permits a more flexible definition of stress and a wider class of ``stressors" including stress defined in terms of  a number of extreme outcomes.  The difference between the stressed and ordinary expectation is defined as the stress risk associated, called \pr\ where P stand for psi,  the function $\psi$ modelling the stress.

@@

\cite{brownlees2015} define stress by conditioning on an absolute cutoff of arbitrary size and length. With time dependent volatility or uncertainty, absolute cutoffs  are less meaningful and our development suggests  it is  useful to specify conditional behaviour in percentile terms relative to current market conditions. This yields a sharper focus on the incremental impact of further stress and permits a more incisive view of the  implications from SRISK numbers. These extensions provide additional insights into the sources and economic nature of for example systemic risk. The measures provide potentially new and improved ways of anticipating episodes of heightened systemic risk. Their practical use can be expected to help regulators monitor risk including systemic risk and contagion in timely fashion,   facilitating remedial action where necessary.

@@

The nature and usefulness of our measures are demonstrated using publicly available daily financial data for the eight Australian banks detailed in \tref{eightbanks} spanning the period from  3 April 2000 through to 1 December 2014.  The data is described in detail in \aref{data}.  Prices, adjusted for dividends are plotted in \fref{prices}.  Prices are combined with number of shares to derive total equity. Total debt for each firm is also collected from annual accounting reports.

Remaining sections are structured as follows. Section \ref{litrev} briefly discusses related literature. Section \ref{capshort} defines current and future  capital shortfall similarly as \cite{brownlees2015} under a simple Basel II regulatory framework. The definition of systemic risk used by \cite{brownlees2015} is discussed, refined and improved in \sref{srisk}. Applications to Australian bank data are discussed in \sref{simulate} and \sref{simulate1}. Section \ref{aggregate}  discusses the aggregation of  stresses across firms with and without allowance for merging or diversification. Section \ref{monitoring} displays stress calculations as they would proceed in real time.   Section \ref{riskmethod} offers an alternative modelling approach, based on assets.  Section \ref{conclude} concludes.

@@

\begin{figure}[htbp]
\label{prices}
\begin{center}
 \begin{tabular}{cc}
      \resizebox{55mm}{!}{\includegraphics{figures/fig1a.pdf}} &
      \resizebox{55mm}{!}{\includegraphics{figures/fig1b.pdf}}\\
    \end{tabular}
\caption{Daily stock  prices of four major (left panel) and four minor (right panel) Australian banks 2000--2014.  Price series normalised to start at 1.}
\end{center}
\end{figure}

@@

\cite{brownlees2015}  develop empirical methodology to construct SRISK measures. SRISK depends on the firm's size, leverage and its LRMES. The LRMES is obtained by assuming a dynamic process for the joint distribution of firm and market returns. \cite{brownlees2015} use  the standard GARCH-DCC model of \cite{engle2002dynamic} with threshold ARCH volatilities on the basis that this represents a good trade-off between model complexity and prediction accuracy. The LRMES is computed as the Monte Carlo average of simulated multi-period returns,  conditional on the return being worse than the cut-off level chosen to identify a financial crisis. Using a sample of large US financial firms,  \cite{brownlees2015} show the practical usefulness of their measure in three ways: (i) SRISK rankings identify systemically risky US banks during the GFC; (ii) pre-crisis SRISK helps predict capital injections by the Fed Reserve; (iii) aggregate SRISK provides early warning of declines in industrial production and higher unemployment.

\cite{Engle2015} extend the model in \cite{brownlees2015} to incorporate global, country and industry effects. This extended model makes  use of the \citep{Engle2014dcb} dynamic conditional beta model. Their empirical methods are able to provide information about the relative systemic importance of industry type and country identity. For instance, they find  that systemic risk in Europe during the GFC was predominantly due to banks while France and the UK recorded the largest country-level SRISK numbers.

\cite{adrian2011covar} propose an alternative measure of systemic risk  emphasising the co--dependence of financial firms and the importance of risk spillovers within the financial sector. They introduce CoVaR$_i$ which computes the Value--at--Risk (VaR) of the entire financial system, conditional on institution $i$ being in distress. Distress is defined as the state where the institution is exactly at its VaR level. \cite{Girardi2013} improve CoVaR by conditioning on the institution being at most at its VaR. This generalisation is useful as it takes into account the severity of tail losses and facilitates back--testing of CoVaR.

@@

Empirical estimates of SRISK  requires a model for the joint distribution of returns of individual firms and the market. Many of these papers use \cite{engle2002dynamic}'s GARCH--DCC model aiming to capture the time-varying dynamics of the return (co)variances in a feasible manner. While we also use this model in our empirical analysis, we emphasize that our approach can utilise any appropriate model for simulating the joint distribution of firm and market returns going forward.

\section{Capital shortfall, leverage and future shortfall}\label{capshort}

@@

The definition of capital shortfall in \eref{shortfall} is restrictive if not simplistic.   It is used here to conform to the previous literature and provide an easily accessible  platform to the key results of this paper,  without becoming entangled in precise and perhaps more realistic definitions of shortfall.   \sref{riskmethod} deals with a more realistic and intricate definition.

@@

\begin{figure}[htbp]
\begin{center}
 \begin{tabular}{cc}
      \resizebox{55mm}{!}{\includegraphics{figures/fig2a.pdf}} &
      \resizebox{55mm}{!}{\includegraphics{figures/fig2b.pdf}}\\
    \end{tabular}
\caption{Adjusted log--leverages for four major (left panel) and four minor (right panel) Australian banks from the beginning of 2003 through to end of 2014.  All banks contravene the threshold (corresponding to the zero horizontal) around the start of 2009.}\label{Bloglev}
\end{center}
\end{figure}

@@

The  future capital shortfall is $S^+$, the positive part of $S$:
\be{bs}
S^+ = kd (1-\e^{r-\ell})^+=\left\{\begin{array}{lr} 0\ , & r\ge \ell\ ,\\ kd (1-\e^{r-\ell})\ , & r<\ell\ .\end{array}\right.
\ee
Thus $S^+$ is $kd$ times a put on the return $\e^{r-\ell}$ with strike 1.  Default put options similar to \eref{bs} have been discussed in the insurance literature as critical to an evaluation of a firm:  see for
example \citet{merton1977analytic}, \citet{doherty1986price}, \citet{cummins1988risk}, \citet{myers2001capital} and \citet{sherris2006solvency}.

To appreciate the behaviour of $S$ and $S^+$, \fref{simulation}   displays two snapshot outputs from projections generated as described  in \aref{garchdcc}:  6000  simulated one month ahead projected returns for  CBA and the wider market, on  two dates: the first trading day in January 2009 and the first trading day in December 2014.  The CBA returns are used to calculate the future shortfall per units $kd$ as in \eref{fshortfall}.  Both panels use the same horizontal and vertical scales.   Based on the available data at those two points in  time, policy makers and regulators faced entirely different projections.   The scatter of dots are the forward simulations.  Note there is no hindsight bias as the model at each time point is based on the available data to that point in time.     In the left panel $S>0$ for most scenarios.    In the right panel $S<0$ for any conceivable market scenario.

 The black dots in each panel indicate the actual outcome after one month.    In the left panel the outcome is a decline in both  the market and CBA stock price.    In the right panel there is slight decline in the stock price, and a more substantial market downturn.    Thus at the beginning of January  2009 the one month forward projection for  CBA was far from compliance, while in December 2014 the one month forward projection is of complete compliance.

The two panels  display very different volatility and slopes. In January 2009 both CBA and the market return distributions are highly volatile and correlated. The correlation remains strong in December 2014 but with less return volatility.  Subsequent sections of this paper use time series of these  snapshots  to compute cross sectional and longitudinal baseline and systemic stresses.

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=12cm]{figures/figCBA.pdf}
\caption{Forecast bivariate distribution of future shortfall $S$ per unit $kd$  for CBA (vertical axis) and market rate of return (horizontal axis) at start of January 2009 (left panel)  and December 2014 (right panel). Note scales in both panels are the same, the relatively large volatility in the left panel, and the left skew in the  marginal distributions.  Black dots indicate actual  outcome at the end of each month.}\label{simulation}
\end{center}
\end{figure}

\section{Improving SRISK for systemic risk monitoring}\label{srisk}

 \cite{brownlees2015} defines  systemic risk for a group of firms  at a particular point of time as
\be{esrisk}
\sr\equiv \sum_i \left\{\Es(S_i)\right\}^+ \ ,
\ee
where $S_i$ refers to the future shortfall in firm $i$.  Here, as before, $^+$ indicates the ``positive part"   and  $\Es$ denotes expectation given a major general market downturn. Hence the expected capital shortfall (allowing surplus offset) is computed from \eref{fshortfall} assuming a market downturn and added across all firms. Firms with an expected capital surplus under stress are ignored.

The systemic risk of firm $i$ at a particular point of time is  \citep{brownlees2015} the proportional contribution to \eref{esrisk}
\be{sriskperc}
\sr_i\equiv\frac{\{\Ex(S_i)\}^+}{\sr}\ .
 \ee
Large $\mathrm{SRISK}_{i}$ indicates firm $i$ is systemically important: it holds a high proportion of the total debt, and it is likely to heavily breach the Basel capital requirement compared to remaining other firms.  Expression \eref{sriskperc} depends on $k$ through each of the adjusted log--leverages $\ell_i$.   Given a general market downturn, the values $\{\Es(S_i)\}^+$  in \eref{sriskperc} are known:  there is no uncertainty except for possible  uncertainty in estimating the stressed conditional  expected value.

A more sensitive measure results when \eref{sriskperc} is based on $\Es(S_i^+)$ rather than $\{\Es(S_i)\}^+$.   In many cases $\Es(S_i)=0$  and hence insensitive to actual shortfalls.   Further, the definition of $\Es$ is readily generalised to encompass more flexible stress specifications.   For example ``cutoff"  market downturns such as 10\%  are more easily achieved  in a highly volatile environment implying the stress response takes on different meanings depending on volatility.  Finally, as shown below, the stressed expectation $\Es$ is composed of two parts, so--called baseline risk and change in expectation risk caused by the actual stress event.

\subsection{Improved systemic risk measurement framework}
The  proposed improved framework assumes a response variable such as capital shortfall $S$ or $S^+$ for a firm or group of firm subjected to stress.  For notational convenience assume the response of interest is $S$ although this can be replaced with $S^+$ or  other function of $S$.  The improved framework is built up from the following parts:
\bi
\i  There exist a collection of scenarios labelled $\omega$ where  $\omega$ discrete or continuous.   Scenarios $\omega$ are systemic if they have potential impact on many firms.  The ``natural" probability of scenario $\omega$ is $f(\omega)$.   If $\omega$ is continuous then $f(\omega)$ is interpreted as a probability density.

\i  A stress function $\psi(\omega)\ge 0$ is defined on the  scenarios $\omega$ with  $\E(\psi)=1$.

\i  Baseline risk is defined as the ordinary expectation
$$
\br\equiv \E(S)\equiv\sum_\omega f(\omega) \E(S|\omega)\ ,
$$
  If $\omega$ continuous then the sum is interpreted as an integral.

\i Stressed expectation  is
\be{formula}
\Es(S) \equiv \sum_\omega \psi(\omega) f(\omega)\E(S|\omega)=\E\{\psi\E(S|\psi)\}=\E(\psi S)=\E(S)+\cov(S,\psi)\ ,
\ee
where the last equality follows since $\E(\psi)=1$.  The import of $\psi(\omega)$ is to change the natural probabilities $f(\omega)$ to ``stressed" probabilities $\psi(\omega)f(\omega)$.   Note $\sum_\omega\psi(\omega) f(\omega)=\E(\psi)=1$. 
 \i $\psi$--risk is defined as the difference between stressed risk and baseline risk
 $$
 \pr \equiv \Es(S)-\E(S) = \cov(S,\psi)\cq \Es(S)=\br+\pr\ .
 $$
\ei

\subsection{Practical stress functions}
The simplest example is where $\psi(\omega)=0$ except for a single  scenario $\omega$ where it is equal to $1/f(\omega)$.   In this case all probability is transferred to the single scenario $\omega$ and $\Es(S)=\E(S|\omega)$.  The conditional expectation is often computed with a spreadsheet.

A richer example is where $\omega$ is the percentile of a variable such as the overall market return, measured relative to the current  market return distribution.   Then $f(\omega)$ is the uniform density on the unit interval.   If 
$$
\psi(\omega)=n\{1-(1-\omega)^{n-1}\}\ ,
$$
then $\psi$ is the density of the worst percentile outcome in $n$ independent trials.   In this case \pr\  corresponds to the increase in risk when the general market has its worst outcome in $n$ independent trials given the current return distribution.  This stress function  is used to study stress in Australian banks in \sref{simulate1}.  If $n=1$ then $\psi(\omega)=1$, there is no stress, and $\Es(S)=\E(S)$ and \pr=0.

Another example, close to that implemented in \cite{brownlees2015} is where $\omega$ is a percentile with $\psi(\omega)=1/c$ for $\omega<c$ and 0 otherwise.   In this case  $\Es(S)=\E(S|\psi<c)$ and \pr\  is the difference between the   tail and ordinary expectation.
More general stressed expectations of the form of \eref{formula} are discussed in \cite{furman2008weighted1} and \cite{choo2010determining}.

\subsection{BRISK and PRISK properties and associated measures}

Both \br\ and \pr\ are linear and aggregate over firms:
$$
\br\left(\sum_iS_i\right) = \sum_i\br\left(S_i\right)\cq\pr\left(\sum_iS_i\right) = \sum_i\pr\left(S_i\right)\ .
$$
Linearity is obvious for \br\ and linearity for \pr\  follows from the linearity of covariance.

@@

\section{Australian bank stress forecasts}\label{simulate1}
